
\cvsection{Education}
\cvevent{BSc. Electrical Engineering}{University of Alberta}{ September 2017 to April 2021}{}
\begin{itemize}
    \item Degree confer in June 2021
    \item Eligible to register as a Member-in-training with APEGA
\end{itemize}
% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Projects}
\cvproject{Engineering Capstone - Mesh Messaging System}
\begin{itemize}
\item Mesh communication system with the goal of offering communication over a kilometer or more. 
\item Phones connect to mesh points and use an app to send messages over this network.
\item This goal is to allow communication over a distance when cellular service is not available or unreliable.
\end{itemize}
\cvproject{Personal File Storage Server}
\begin{itemize}
\item Arch Linux is the operating system of choice for both the personal computer and server functions.
\item Built from parts found at the computer store.
\item Plex software is used for the media streaming functionality
\item "Syncthing" software for file synchronization.
\item File systems like ZFS, BTRFS, and Windows Storage Spaces are used for data redundancy in case of a hardware failure.
\end{itemize}
\cvproject{Personal Website}
\begin{itemize}
\item Personal website showcasing what I have to offer. Can be seen at lyndeno.ca.
\end{itemize}

\cvsection{TECHNICAL SKILLS}
\begin{itemize}
\item MATLAB, Bentley Microstation, Xilinx Vivado, MS Office, Microchip AVR
\item C, Powershell, VBA, FreeRTOS, AVR C, HTML, Rust(Beginner Level)
\item Deep understanding of Linux and Windows
\end{itemize}

\cvsection{PERSONAL SKILLS}
\begin{itemize}
\item Ability to work under pressure.
\item Comfortable working independently or with a team.
\item Ability to take initiative to solve complex problems.
\item Extremely familiar with computers and can easily adapt to use new software and hardware devices.
\end{itemize}